MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident angle

### 2022-01-24 paper.tex
updates

The sampling calorimeter was designed as alternating 1-mm-thick lead plates for passive converters and 5-mm-thick strips of the plastic scintillator for active counters. The cross section of the lead plate and the scintillator is 525 mm $\times$ 525 mm and 15 mm $\times$ 525 mm, respectively. Strips are alternatively aligned along $x$ and $y$ direction as shown in Fig.~\ref{fig:det_conf}. The total number of alternating layers is 105, which corresponds to 20$X_{0}$ to make it possible to absorb whole products from the EM shower ranging from 100 MeV to few GeV energy.

@@

\begin{figure}[!hbt]
\includegraphics[width=0.6\textwidth]{figures/layer-event.jpg}
\caption{  \textcolor{red}{plots should be updated} The angular resolution for 1 GeV $\gamma$ with $\theta=$~10~deg as a function of the number of training samples with different strip widths using the first 24 layers or the full layers. }
\label{fig:multi-parameter}
\end{figure}

>>>>

The sampling calorimeter was designed as alternating 1-mm-thick lead plates for passive converters and 5-mm-thick strips of the plastic scintillator for active counters. Strips are alternatively aligned along $x$ and $y$ direction as shown in Fig.~\ref{fig:det_conf}. The cross section of the lead plate and the scintillator is 525 mm $\times$ 525 mm and 15 mm $\times$ 525 mm, respectively. The material for the scintillator strip is polyvinyltoluene. The total number of alternating layers is 105, which corresponds to 20$X_{0}$ to make it possible to absorb whole products from the EM shower ranging from 100 MeV to few GeV energy.

@@

\begin{figure}[!hbt]
\includegraphics[width=0.6\textwidth]{figures/layer-event.jpg}
\caption{ The angular resolution for 1 GeV $\gamma$ with $\theta=$~10~deg as a function of the number of training samples with different strip widths using the first 24 layers or the full layers. }
\label{fig:multi-parameter}
\end{figure}
